---
title: "Day5_Journey"
Author: "Chen-Chia Ku"
date: "2024-11-05"
output: html_document
editor_options: 
  chunk_output_type: console
---
# A Big Note

This code was original from [Andrew Heiss](https://doi.org/10.59350/rgwda-0tv16). I revise it into my version, my journal and my trips in United State.


# Setwd
```{r}
setwd("D:/Drive/6_Rworld/30DayMapChallenge")

```

# Library

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)     # ggplot, dplyr, and friends
library(sf)            # Handle spatial data in R in a tidy way
library(tigris)        # Access geographic data from the US Census
library(tidygeocoder)  # Automated geocoding
library(osrm)          # Access OSRM through R
library(ggrepel)       # Nicer non-overlapping labels
library(glue)          # Easier string interpolation
library(scales)        # Nicer labeling functions
library(patchwork)     # Combine plots nicely
library(ggspatial)     # Nicer map features like scale bars
library(NatParksPalettes)
library(ggpubr)
```

# 1. United State Data
```{r}
us_states <- states(resolution = "20m", year = 2022, cb = TRUE)

lower_48 <- us_states %>% 
  filter(!(NAME %in% c("Alaska", "Hawaii", "Puerto Rico")))
```

# 2. My Travel Data
```{r}
stops_raw <- tribble(
  ~direction,  ~city,
  "Stop",     "Logan, Utah", 
  "Pass",     "Baker City, Oregon", 
  "Stop",     "Carson, Washington", 
  "Stop",     "Portland, Oregon", 
  "Stop",     "Carson, Washington",
  "Pass",     "Redmond, Oregon",  
  "Pass",     "Mount Shasta, California", 
  "Pass",     "Sacramento, California", 
  "Stop",     "Yosemite NP, California",
  "Pass",     "Tenya Lake, California",  
  "Pass",     "Tioga Pass Rd, California", 
  "Pass",     "Benton, California",
  "Pass",     "Tonopa, Nevada", 
  "Pass",     "Ely, Nevada", 
  "Pass",     "West Wendover, Nevada",
  "Stop",     "Logan, Utah",  
  "Pass",     "Cedar City, Utah", 
  "Stop",     "Cedar Breaks National Monument, Utah",
  "Stop",     "Logan, Utah", 
  "Pass",     "Garden City, Utah",
  "Pass",     "Geneva, Idaho", 
  "Pass",     "Alpine, Wyoming", 
  "Pass",     "Jackson, Wyoming",
  "Pass",     "Moran, Wyoming",  
  "Stop",     "Yellowstone NP, Wyoming",
  "Stop",     "Gardiner, Montana",
  "Pass",     "Tower Junction, Wyoming",
  "Pass",     "Canyon Village, Wyoming",
  "Stop",     "Grand Teton NP, Wyoming",
  "Pass",     "Alpine, Wyoming", 
  "Pass",     "Grace, Idaho",
  "Stop",     "Logan, Utah"
)  %>% 
  mutate(direction = fct_inorder(direction))


```

## 2.1. My Address
```{r}
stops_addresses <- tribble(
  ~city, ~address,
  "Yosemite NP, California", "6107 CA-120, Groveland, California",
  "Yellowstone NP, Wyoming", "Old Faithful, Teton County, Wyoming",
  "Grand Teton NP, Wyoming", "103 Headquarters Loop Moose,Wyoming"
)


```

## 2.2. Join the Address
```{r}
stops_to_geocode <- stops_raw %>% 
  left_join(stops_addresses, by = join_by(city)) %>% 
  mutate(address = coalesce(address, city))

```

# 3. Get the longitude and latitude from geocode()

This is the most cool thing that I am so excited, so lazy, so happy to have that coordinate automatically. 

```{r}
stops_geocoded <- stops_to_geocode %>% 
  geocode(address, method = "osm") %>%
  st_as_sf(coords = c("long", "lat"), crs = st_crs("EPSG:4326"))

```

## 3.1. Made my stop unique
```{r}
all_stops_unique <- stops_geocoded %>%
  filter(direction=="Stop") %>%
  distinct(city,.keep_all=T)
#  slice(1:(n() - 1))

```

# 4. Get the path
```{r}
routes_raw <- stops_geocoded %>% 
  select(-address) %>% 
  rename(
    origin_geometry = geometry,
    origin_city = city
  ) %>% 
  mutate(
    destination_geometry = lead(origin_geometry),
    destination_city = lead(origin_city)
  ) %>% 
  filter(row_number() != n())

```

```{r}
routes_geocoded_raw <- routes_raw %>% 
  rowwise() %>% 
  mutate(route = osrmRoute(
    src = origin_geometry, 
    dst = destination_geometry)
  )

```


```{r}
routes_geocoded <- routes_geocoded_raw %>% 
  unnest(route, names_sep = "_") %>% 
  st_set_geometry("route_geometry") %>% 
  mutate(
    distance_miles = km_to_miles(route_distance),
    distance_text = fmt_miles(distance_miles),
    duration_text = fmt_duration(route_duration)
  )
```

# 5. Get the State that I have traveled 

```{r}
states_crossed_through <- st_intersection(
  st_transform(lower_48, st_crs(routes_geocoded)),
  routes_geocoded
)


states_crossed_through %>% 
  select(STATEFP, NAME, direction)

unique(states_crossed_through$NAME)

# Create a column that flags if the state is cross through
lower_48_highlighted <- lower_48 %>% 
  mutate(visited = NAME %in% unique(states_crossed_through$NAME))

```

# 6. Mapping

## 6.1 Adjust my boundary
```{r}
boundary <-st_sfc(st_point(c(-121, 24)), st_point(c(-104, 51)), crs = 4326) %>%
    st_transform(crs = "ESRI:102003")

```

## 6.2 Mapping part
```{r}

RT <- ggplot() +
  geom_sf(data = lower_48_highlighted, aes(fill = visited), color="grey60") +
  geom_sf(data = routes_geocoded, color = "#5e0010") +
  geom_sf(data = all_stops_unique) +
  geom_label_repel(
    data = all_stops_unique,
    aes(label = city, geometry = geometry),
   stat = "sf_coordinates", seed = 100,
    size = 2, segment.color = clrs[3], 
   direction="both", min.segment.length = 0
  ) +
  annotation_scale(
    location = "bl", bar_cols = c("grey30", "white"),
    unit_category = "imperial"
  ) +
  scale_fill_manual(values = c("grey90", "pink"), guide = "none") +
  coord_sf(xlim=c(as.matrix(boundary[[1]])[1],
                  as.matrix(boundary[[2]])[1]),
           ylim=c(as.matrix(boundary[[1]])[2],
                  as.matrix(boundary[[2]])[2]),
           crs = st_crs("ESRI:102003")) +  # Albers
  theme(panel.background = element_rect(color="black", fill="NA"),
        panel.grid = element_line(color = "grey"),
        axis.title = element_blank(),
        axis.text.x = element_text( size=5, vjust=3),
        axis.text.y = element_text(angle = 270, vjust = 12, hjust=0.5, size=5), 
        axis.ticks = element_blank(), 
        legend.position = "none")
RT
```

```{r}
ggexport(RT , filename = "2024_Challenge/Output_Map/Day5_Journey_test.png", width = 7000, height=10000, res=1200)

```

# 7. Get my whole USA
```{r}
USA <- ggplot() +
  geom_sf(data = lower_48_highlighted, aes(fill = visited), color="grey60")+
  scale_fill_manual(values = c("grey95", "pink1"), guide = "none") +
  coord_sf(crs = st_crs("ESRI:102003"))+
  theme(panel.background = element_rect(color="black", fill="NA"),
        panel.grid = element_line(color = "grey"),
        axis.title = element_blank(),
        axis.text.x = element_text( size=5, vjust=3),
        axis.text.y = element_text(angle = 270, vjust = 12, hjust=0.5, size=5), 
        axis.ticks = element_blank(), 
        legend.position = "none")
```

```{r}
ggexport(USA , filename = "2024_Challenge/Output_Map/USA_test.png", width = 10000, height=7000, res=1200)

```



